Dissecting the interaction between skill level and mental templates in Late Acheulean handaxe morphology: Archaeological and experimental insights

### 2022-11-27 manuscript/manuscript.Rmd
changed the caption of figure 4.

```{r PCcorrelation, echo=FALSE, out.width = '100%', fig.align='center', fig.cap="A scatter plot showing the correlation between PC1 and PC2 respectively in the groups of Boxgrove (left, n=326), expert (middle, n=10), and novice (right, n=132)."}
knitr::include_graphics(here::here("figure/Fig4.png"))
```

>>>>

```{r PCcorrelation, echo=FALSE, out.width = '100%', fig.align='center', fig.cap="A scatter plot showing the correlation between PC1 and PC2 respectively in the groups of Boxgrove (left, n=326), expert (middle, n=10), and novice (right, n=132). The upper left area in each individual plot display statistical reporting from a frequentist perspective, including the student-t test statistics, p-value, Pearson correlation coefficient, confidence interval, and sample size. The lower right area in each individual plot display statistical reporting from a Bayesian perspective, including the natural logarithm of Bayes factor, posterior type and estimate, credible interval, and prior type and value. "}
knitr::include_graphics(here::here("figure/Fig4.png"))
```
